Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-28 Paper/RSVOptimization.rnw
Creeping up on 250 words

\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and leads to hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe, effective, and costly immunoprophylaxis. The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants, and only during the RSV season. The current guidelines do not recommend spatial or temporal adjustments to the immunoprophylaxis regimen outside of Florida. In this study, we investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.

\abstractsection{Methods}We obtained weekly ZIP-code-level counts of RSV-associated hospital admission in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We fit smoothed curves to these admission counts and thus estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates (but unchanged duration).

\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in timing of RSV seasons are superior to the AAP-recommended regimen. Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint. In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).

>>>>

\abstractsection{Background}Respiratory syncytial virus (RSV) causes seasonal respiratory infection with potentially serious complications in children and hospitalization rates of up to 50\% in high-risk infants. Palivizumab provides safe, effective, and costly immunoprophylaxis. The American Academy of Pediatrics (AAP) recommends palivizumab only for high-risk infants, and only during the RSV season. Outside of Florida, the current guidelines do not recommend regional adjustments to the immunoprophylaxis. We investigate the benefits of adjusting the RSV prophylaxis regimen in Connecticut based on the spatial variation of RSV incidence.

\abstractsection{Methods}We obtained weekly RSV-associated hospital admissions by ZIP-code in Connecticut between \Sexpr{formatMonth(startDate)} and \Sexpr{formatMonth(endDate)}. We estimated the fraction of all RSV cases in Connecticut occurring during the period of protection offered by RSV immunoprophylaxis (``preventable fraction'') under the AAP guidelines. We then used the same model to estimate protection conferred by immunoprophylaxis regimens with alternate start dates, but unchanged duration.

\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen. Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint; in comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).
